\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}
\author{K.M.J. Jacobs}
\title{Path Integral Control Theory}

% Set all of these to false for the final document
\newif\ifrequirements
\requirementstrue
%\requirementsfalse

\begin{document}
\maketitle

\ifrequirements
\color{red}
\textbf{Document requirements shown by flag \texttt{requirementstrue}.}
\textbf{Set flag \texttt{requirementsfalse}.}

\color{blue}
\section{Guidelines for ML assignments}
Note: All reports should be handed in before the end of January 2017. Hard deadline is \textbf{January 31 at 23.59}. Any questions about the below points please contact me (Hans-Christian Ruiz). For the assignments please refer to the ML course page.

\subsection{Requirements to hand in the reports}
\begin{itemize}
\item Hand in each report as a SINGLE document with all figures, code, etc (other "extra" files will not be considered). Hand in printed in my post box (Ruiz, wing 8, ground floor).
\item In addition, hand in the code that can be run stand-alone. Send us an email with a zip-file containing the codes for all assignments. The zip-file should be named with the last names of all group members. Each code in the zip-file should be named as AssignmentName where AssignmentName is: Ising, BM, MNIST, Lasso, Control
\item Your name on each report and the name of the corresponding code file in the zip-file that you sent us via email.
\item The report should be well structured and clear.
\item Figures need to have a caption explaining in detail what they show. 6. No more than 8 pages (excluding references and code) with 12 pts font.
\end{itemize}

\subsection{Minimal requirements of the content}
The report for each exercise addresses following points:
\begin{itemize}
\item Introduction: summarizes the underlying theory and algorithm(s). It should be a short description of the theoretical background and expla- nation of the method considered (no more than a page!).
\item Problem statement: Itemizes a number of research questions that you address
\item Results: Detailed description of the different numerical studies that you have performed with plots and specification of the parameter settings (a) Precise, clear description of what you have done, with the used formulas and the argumentation of why you have done it; e.g. what measure of convergence you used, are there alternatives? (b) Figures with a detailed explanation of what the relevant results are (c) An analysis of the results (for example: is the result as expected? why?/why not? what does the result mean? etc...)
\item General discussion/Conclusions: A summary of the main findings and conclusions (no more than half page!)
\item Appendix: If the exercise requires to write a code, add the code in the appendix. The code should have the following characteristics (a) Well documented, comments! (b) Suitable structure for readability, e.g. indentation, proper (mnemonic) variable naming. 6. Note: The code will not be evaluated based on whether it is optimized or not, only if it is clearly readable. But, IT MUST RUN STAND- ALONE!
\end{itemize}

\color{black}
\fi

\newpage
\section{Introduction}


\section{Problem statement}
\subsection{Controlled random walk}
In the controlled random walk problem, the rate of change of the state is defined as follows:

\begin{equation}
dx = u dt + d\xi
\label{eq:crw_dx}
\end{equation}

The state has initial position $x$ at $t = 0$. The noise variance is $\langle d \xi^2 \rangle = \nu dt$.

There are two targets at $t = T$ at locations $x = \pm 1$. The end-cost function $\phi$ is defined such that it has delta peaks at the targets:

\begin{equation}
\phi(x(T)) = \begin{cases}
0 & x(T) = \pm 1\\
\infty & \mbox{otherwise}
\end{cases}
\label{eq:crw_phi}
\end{equation}

The optimal control for this problem satisfies:

\begin{equation}
u^{*}(t, x) = \frac{\tanh(x / (\nu (T - t)) - x}{T - t}
\label{eq:crw_u}
\end{equation}

The following research questions are discussed for the controlled random walk problem in this report:
\begin{itemize}
\item How does the optimal control depend on parameters $\nu$ and $T$ numerically?
\item How does the delayed choice mechanism work?
\end{itemize}

\subsection{Mountain car problem}
The following research questions are discussed for the mountain car problem in this report:
\begin{itemize}
\item What is the optimal control policy for this problem?
\end{itemize}

\section{Results}
\subsection{Controlled random walk}
\subsubsection{How does the optimal control depend on parameters $\nu$ and $T$ numerically?}


\subsubsection{How does the delayed choice mechanism work?}

\subsection{Mountain car problem}

\section{Discussion}
\subsection{Controlled random walk}
\subsection{Mountain car problem}

\section{Conclusion}
\subsection{Controlled random walk}
\subsection{Mountain car problem}

\newpage
\section{Appendix}
\end{document}